\begin{cnabstract}
接触网是指通过集电装置（集电靴、受电弓等）想电力牵引单元提供电能的机电系统。接触网是电气化轨道交通的重要组成部分，是电气化轨道交通的标志性供电设施，是一特殊的电力输电线路。接触网的特殊性在于接触网是集电装置的滑道，除应具备电力输电线路的全部特性和要求外，还与集电装置存在几何、电气、机械和材料匹配关系。
我们组借助《接触网工程》等相关书籍对锚段长度、锚段张力、跨距、咽喉区等进行了计算，还对有载承力索的张力-温度曲线、有载·承力索弛度－温度曲线、接触线弛度温度曲线等图像进行了绘制，对缓和曲线接触线最大偏移值、支柱容量进行了校验，对软横跨进行了预制，并最终绘制出了渠县车站放图、站场和区间平面图、咽喉区放大图等。
在完成课程设计的过程中，小组成员各司其职，都完成了自己的任务。使用了AutoCAD软件进行了图像的绘制，并进行了选型。考虑了实际情况与安全，留了裕量。

\end{cnabstract}
\vspace{1em}\par

\cnkeywords{接触网设计;图像绘制;autoCAD软件}

\begin{enabstract}
Catenary network refers to an electromechanical system that provides electric energy to electric traction units through current collection devices (collector shoes, pantographs, etc.). The catenary is an important part of electrified rail transit, an iconic power supply facility for electrified rail transit, and a special power transmission line. The particularity of the catenary is that the catenary is the slideway of the current collecting device. In addition to having all the characteristics and requirements of the power transmission line, it also has a geometric, electrical, mechanical and material matching relationship with the current collecting device.
Our group used relevant books such as "Cennel Engineering" to calculate the length of the anchor section, tension of the anchor section, span, throat area, etc., and also calculated the tension-temperature curve of the load-bearing cable and the relaxation of the load-bearing cable. The temperature-temperature curve, contact line relaxation temperature curve and other images were drawn, the maximum offset value of the relaxation curve contact line and the pillar capacity were verified, the soft span was prefabricated, and finally the Quxian station layout was drawn. Figures, station and section floor plans, enlarged views of the throat area, etc.
In the process of completing the course design, the team members performed their duties and completed their tasks. AutoCAD software was used to draw images and select models. Taking into account the actual situation and safety, a margin was left.
\end{enabstract}
\vspace{1em}\par

\enkeywords{Catenary design; image drawing; autoCAD software}